Online (Bandit) Policy Selection for EASY-Backfilling

### 2017-03-30 paper/paper.tex
all

In order to simulate how the simulation strategy for selecting policies would work on non simulated traces, we randomly introduce noise in the estimate of the waiting time defined by Eq.~\ref{eq:cost-exact}

>>>>

In order to simulate how the simulation strategy for selecting policies would work on non simulated traces, we randomly introduce noise in the estimate of the waiting time defined by Eq.~\ref{eq:cost-exact} by rescaling, either dow or up, the waiting time of jobs obtained by simulation:
%
\begin{equation}
\label{eq:cost-exact}
w_{\mbox{noisy}}(t;P_i) = \sum_{j=1}^{l(\Delta_t)} \rho \mbox{Wait}_j^{P_i}
\end{equation}
%
